Ontology Matching with word2vec

### 2016-04-11 Paper/Draft.tex
Renamed possibilities to considered implementations

 \subsection{Possibilities} % Rename please

@@

 It is in principle possible to weigh False Positives and False Negatives differently, but this is not done in practice. To make the results of this study easily comparable to others, equal weights will be used.
 \subsection{Data}
 The data used comes from a list of data sets that the OAEI provides. % Zoek paper, misschien http://www.sciencedirect.com/science/article/pii/S1570826813000188
 %Hoeveel preprocessing moest ik doen
 Every data set contains two ontologies that need to be aligned and a ground truth alignment. The goal is straightforward: find the alignment given only the ontologies and whatever outside resources are needed.

@@

 \section{Results}

>>>>

 \subsection{Considered implementations}
 In this section, I will discuss the different implementations that were made of the algorithm. All implementations use the same basic algorithm in different ways by taking into account the context in different ways. All of these implementations were tested and the results can be found in \ref{results}. Some implementations are extensions of other implementations, but all implementations are mentioned for completeness and to enable explanation of the source of improvements.

@@

 It is in principle possible to weigh False Positives and False Negatives differently, but this is not done in practice. To make the results of this study easily comparable to others, equal weights will be used.
 \subsection{Data}
 The data used comes from a list of data sets that the OAEI provides. % Zoek paper, misschien http://www.sciencedirect.com/science/article/pii/S1570826813000188
 %Hoeveel preprocessing moest ik doen
 Every data set contains two ontologies that need to be aligned and a ground truth alignment. The goal is straightforward: find the alignment given only the ontologies and whichever outside resources are needed.

@@

 \section{Results} \label{results}
